Predictive Modeling of Drinking Water Treatment Process Chemical Doses

### 2025-12-09 Paper Draft.Rmd
Redid variable names for plotting section

rwar_dosing <- read.csv("RWAR_dosing_cleaned.csv")
rwar_dosing$Timestamp <- ymd(rwar_dosing$Timestamp)

plot_pH <- ggplot(rwar_dosing, aes(x = Timestamp,
                           y = mean_pH,
                           color = mean_pH)) +
  geom_line() + 
  scale_color_gradient(low = 'blue', high = 'red') +
  theme_minimal() +
  ggtitle("Average pH")

plot_polymer <- ggplot(rwar_dosing, aes(x = Timestamp,
                           y = Cationic.Polimer..mg.L,
                           color = Cationic.Polimer..mg.L)) +
  geom_line() + 
  scale_color_gradient(low = 'yellow', high = 'green') +
  theme_minimal() +
  ggtitle("Polymer Coagulant")

plot_FeCl <- ggplot(rwar_dosing, aes(x = Timestamp,
                           y = Ferric.chloride..mg.L,
                           color = Ferric.chloride..mg.L)) +
  geom_line() + 
  scale_color_gradient(low = 'blue', high = 'orange') +
  theme_minimal() +
  ggtitle("FeCl Coagulant")

plot_temp <- ggplot(rwar_dosing, aes(x = Timestamp,
                           y = mean_Temp,
                           color = mean_Temp)) +
  geom_line() + 
  scale_color_gradient(low = 'blue', high = 'red') +
  theme_minimal() +
  ggtitle("Water Temperature")

plot_cond <- ggplot(rwar_dosing, aes(x = Timestamp,
                           y = mean_Conductivity,
                           color = mean_Conductivity)) +
  geom_line() + 
  scale_color_gradient(low = 'purple', high = 'yellow') +
  theme_minimal() +
  ggtitle("Water Conductivity")

plot_turb <- ggplot(rwar_dosing, aes(x = Timestamp,
                           y = mean_Turbidity,
                           color = mean_Turbidity)) +
  geom_line() + 
  scale_color_gradient(low = 'black', high = 'orange') +
  theme_minimal() +
  ggtitle("Water Turbidity")

>>>>

df_lag_incdec <- read.csv("RWAR_dosing_lag_incdec.csv") |>
  mutate(Timestamp = ymd(Timestamp))

plot_pH <- ggplot(df_lag_incdec, aes(x = Timestamp,
                           y = mean_pH,
                           color = mean_pH)) +
  geom_line() + 
  scale_color_gradient(low = 'blue', high = 'red') +
  theme_minimal() +
  ggtitle("Average pH")

plot_polymer <- ggplot(df_lag_incdec, aes(x = Timestamp,
                           y = Polymer_dose,
                           color = Polymer_dose)) +
  geom_line() + 
  scale_color_gradient(low = 'yellow', high = 'green') +
  theme_minimal() +
  ggtitle("Polymer Coagulant")

plot_FeCl <- ggplot(df_lag_incdec, aes(x = Timestamp,
                           y = FeCl_dose,
                           color = FeCl_dose)) +
  geom_line() + 
  scale_color_gradient(low = 'blue', high = 'orange') +
  theme_minimal() +
  ggtitle("FeCl Coagulant")

plot_temp <- ggplot(df_lag_incdec, aes(x = Timestamp,
                           y = mean_Temp,
                           color = mean_Temp)) +
  geom_line() + 
  scale_color_gradient(low = 'blue', high = 'red') +
  theme_minimal() +
  ggtitle("Water Temperature")

plot_cond <- ggplot(df_lag_incdec, aes(x = Timestamp,
                           y = mean_Conductivity,
                           color = mean_Conductivity)) +
  geom_line() + 
  scale_color_gradient(low = 'purple', high = 'yellow') +
  theme_minimal() +
  ggtitle("Water Conductivity")

plot_turb <- ggplot(df_lag_incdec, aes(x = Timestamp,
                           y = mean_Turbidity,
                           color = mean_Turbidity)) +
  geom_line() + 
  scale_color_gradient(low = 'black', high = 'orange') +
  theme_minimal() +
  ggtitle("Water Turbidity")
